Tabular Constraint Learning

### 2016-04-08 Paper/ECAI/tabular.tex
writing the problem statement
Constraint table expanded

    \multicolumn{2}{c}{{\textbf{Tabular Constraint Learning Problem}}}\\
    &\\
    \textbf{Given:} & The set of all groups $\groups$ and the set of Excel  \\
    \phantom{Given:} & constraints $\constraints$ with its dependencies DAG $\dependecies$\\
    \textbf{Find: } & text
  \end{tabular}
\end{framed}

@@

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\ 
    Y = RANK(X)     & $\numeric(G_X) \wedge \integer(G_Y) \wedge \length(G_X) = \length(G_Y)$ & $\begin{array}{r} X \in G_X, Y \in G_Y{:}~\forall i,j \in \nat{:}~(Y_i \leq Y_j \rightarrow X_{Y_i} \leq X_{Y_j}) \\ \wedge~ 1 \leq Y_i \leq \length(G_Y) \end{array}$ \\
    ALLDIFFERENT(X) & $\textual(G_X) \vee \integer(G_X) $ & $X \in G_X{:}~\forall i,j \in \nat{:}~i \neq j \rightarrow X[i] \neq X[j]$ \\
  \end{tabular}
  \caption{Excel Tabular Constraints \sergey{Luc, we need your comments here on the notation of $X,Y$ and $G_X,G_Y$}}
  \label{table:constraints}
\end{table*}

>>>>

    \multicolumn{2}{c}{{\textbf{Tabular Constraint Learning Problem}}}\\
    &\\
    \textbf{Given:} & The set of all groups $\groups$ and the set of Excel  \\
    \phantom{Given:} & constraints $\constraints$ with its dependencies DAG $\dependecies$\\
    \textbf{Find:} & For each constraint $c$ in \constraints all the subgroups of $\groups$ satisfying the \CSignature and \CFunction of $c$
  \end{tabular}
\end{framed}

@@

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    ALLDIFFERENT(X) & $\textual(G_X) \vee \integer(G_X) $ & $X \in G_X{:}~\forall i,j \in \nat{:}~i \neq j \rightarrow X[i] \neq X[j]$ \\
    X = Y & & \\
    FK -> PK & & \\
    R = PRODUCT(FV, FK=PK | PV) & & \\
    FV = FUZZY-LOOKUP(FK, PK, PV) & & \\
    FV = LOOKUP(FK, PK, PV) & & \\
    PERMUTATION(X) & & \\
    R = O1 * O2 & & \\
    R = PROJECT(P) & & \\
     Y = RANK(X)     & $\numeric(G_X) \wedge \integer(G_Y) \wedge \length(G_X) = \length(G_Y)$ & $\begin{array}{r} X \in G_X, Y \in G_Y{:}~\forall i,j \in \nat{:}~(Y_i \leq Y_j \rightarrow X_{Y_i} \leq X_{Y_j}) \\ \wedge~ 1 \leq Y_i \leq \length(G_Y) \end{array}$ \\
    A = PREV(A) + P - N & & \\
    SERIES(X) & & \\
    Y = SUM(X, col) & & \\
    Y = SUM(X, row) & & \\
    R = SUMIF(FK=PK, V) & & \\
    R = SUMPRODUCT(O1, O2) & & \\

  \end{tabular}
  \caption{Excel Tabular Constraints \sergey{Luc, we need your comments here on the notation of $X,Y$ and $G_X,G_Y$}}
  \label{table:constraints}
\end{table*}
